Research Cases

### 2025-12-18 Code/R/Research/cases_research.Rmd
More r3 cases

  if (complex) {
    period_f <- exp
    unit <- 1i
  } else {
    period_f <- cos
    unit <- 1
  }
  N_ones <- rep(1, N)
  ts_range <- seq(from = from, length.out = N, by = by)
  poly_ampl <- apply(poly_ampl_coefs, 2:length(dim(poly_ampl_coefs)), polynom_eval, x=ts_range)
  ts_arr <- poly_ampl * (N_ones %o% ampl) * (N_ones %o% exp(rate)) *
    period_f(N_ones %o% phase + 2 * pi * unit * ts_range %o% freq)

@@

```{r}
((ssa_err_summ[-1, 2] - tssa_err_summ[-1, 2]) / ssa_err_summ[-1, 1]) |> rename(err_diff = best)
```

>>>>

  if (complex) {
    period_f <- exp
    unit <- 1i
  } else {
    period_f <- cos
    unit <- 1
  }
  N_ones <- rep(1, N)
  ts_range <- seq(from = from, length.out = N, by = by)
  poly_ampl <- apply(poly_ampl_coefs, 2:length(dim(poly_ampl_coefs)), polynom_eval, x=ts_range)
  ts_arr <- poly_ampl * (N_ones %o% ampl) * exp(ts_range %o% rate) *
    period_f(N_ones %o% phase + 2 * pi * unit * ts_range %o% freq)

@@

```{r}
((ssa_err_summ[-1, 2] - tssa_err_summ[-1, 2]) / ssa_err_summ[-1, 1]) |> rename(err_diff = best) |> cbind(ssa_err_summ[-1, 1])
```
